---
title: "dtc_rubric_walkthrough"
author: "Group 3"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
editor_options: 
  chunk_output_type: inline
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(urca)
library(dynlm)
library(readxl)
library(forecast)
library(tidyverse)
library(tseries)
library(fpp2)
library(knitr)
library(stats)
library(ggpubr)
library(scales)
library(datplot)
library(kableExtra)
library(ggannotate)
library(lmtest)
library(lubridate)
library(TSstudio)
library(plotly)
library(DT)
```
1. Why do you choose this time series?

2. Why should we care about the forecasts of this time series?

3. The time series has been accurately plotted and appropriately labeled

4. The characteristics of the time series, such as frequency, trends, seasonality, and anomalies, have been clearly described, providing a comprehensive understanding of its temporal behavior.

```{r}

```

The Augmented Dickey-Fuller tests have been accurately performed, and the obtained test results have been correctly interpreted.

```{r}

```

The ACF and PACF correlograms have been accurately plotted, and a coherent explanation is provided to justify the selection of AR or MA process orders based on these correlograms.

```{r}

```

The ACF and PAC correlograms of the residuals from each specification have been accurately plotted. Furthermore, the white noise property of the residuals has been verified using Q-tests. The test results have been correctly interpreted to determine whether the residuals exhibit the characteristics of white noise.

```{r}

```

The model estimation and evaluation results have been accurately summarized in a table format, similar to Table 8.2 on page 214.

```{r}

```

The multistep forecasts, along with their corresponding bands, have been accurately plotted. The interpretation of the results are provided

```{r}

```

For each model, correctly calculate the one-step ahead forecasts, the forecast errors, the loss using quadratic loss function

```{r}

```

The forecast optimality tests, including the mean percentage error (MPE) and informational efficiency tests, have been correctly implemented for each model. Additionally, the mean squared error (MSE) has been accurately calculated and used correctly in choosing models.

```{r}

```

The combined forecasts have been correctly conducted using three linear combination schemes. The weights and MSE of these three combinations of forecasts have been accurately summarized in a table format, similar to Table 9.8 on page 246.

```{r}

```