---
title: "working_hours_analysis_steamlined"
author: "Group 3"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(urca)
library(dynlm)
library(readxl)
library(forecast)
library(tidyverse)
library(tseries)
library(fpp2)
library(knitr)
library(stats)
library(ggpubr)
library(scales)
library(datplot)
library(kableExtra)
library(ggannotate)
library(lmtest)
library(lubridate)
library(TSstudio)
library(plotly)
```

https://fred.stlouisfed.org/series/AWHAE
Our data is FRED creating an index (2007=100) of aggregate weekly hours reported on a monthly basis. The indexes of aggregate weekly hours are calculated by dividing the current month's aggregate hours by the average of the 12 monthly figures, for the base year (2007).

# Data Load 
```{r, echo=FALSE, warning=FALSE}
# Read in Data
working_hours = read_excel("../data/ch10_Weekly_Hours.xls")

# Added as working_hours1 removed the year and month necessary for some functions to run.
working_hours <- working_hours %>%
  mutate(year = year(observation_date),
         month = month(observation_date))

# Create covid and recession indicators associated with time.
working_hours1 <- working_hours %>%
  mutate(year = year(observation_date),
         month = month(observation_date),
         first_difference_index = working_hours$hours_worked_index-lag(working_hours$hours_worked_index)
         )

# Create a time series object
working_hours_ts = ts(working_hours$hours_worked_index, 
                      frequency = 12,
                      start = c(2006, 3)
                      )

# Create First Difference of Hours Worked Index
working_hours_diff = diff(working_hours_ts)

# # Checking for Cumulative Variance
# plot(cvar(working_hours_ts), type = "l")
# 
# # Checking Cumulative variance of difference data
# plot(cvar(working_hours_diff), type = "l") # Looks more stable.
```

# EDA
## Plot Raw Data
```{r, echo = FALSE}
plot_work_hours <- ggplot(working_hours1, aes(x = observation_date, 
                                             y = hours_worked_index)
                          ) +
  geom_line(size = 1) +
  stat_smooth(color = "blue", size =.4) +
  geom_rect(aes(xmin=as.POSIXct('2020-02-01'), xmax=as.POSIXct('2020-04-01'), ymin=-Inf, 
                ymax=Inf),linetype = 'dashed',color="light green", fill = 'light green', alpha=.01) +
  
  geom_rect(aes(xmin=as.POSIXct('2007-12-01'), xmax=as.POSIXct('2008-07-01'), ymin=-Inf, ymax=Inf), 
            linetype = 'dashed',color="light green", fill = 'light green', alpha=.01) +
  geom_hline(yintercept = mean(working_hours1$hours_worked_index), linetype = "dashed", color = "red") +
   scale_x_datetime(labels = date_format("%Y"),breaks = "1 year") +
  labs(x = 'Date', y = 'Indexed Working Hours',
      title = 'Mar 2006 - MAR 2023 Agg. Weekly Work Hours Index Indexed(2007=100)', 
      subtitle =  'Recession(s) highlighed  Red Dashed Line = Time Series Mean') +
  theme(axis.text.y=element_text(face="bold", color="black", size=10, angle=0),
      axis.ticks.y=element_blank(),
      axis.title = element_text(face = "bold", color="black", size=10),
      axis.text.x = element_text(face = "bold", color="black", size=10),
      panel.background =element_rect('White'),
      legend.position = "none")
plot_work_hours

# Interactive plots
ts_plot(working_hours_ts, slider = TRUE,width = 3,
        title = "Mar 2006 - MAR 2023 Agg. Weekly Work Hours Index Indexed(2007=100)")

ggplotly(plot_work_hours)

# Heatmap by year and month raw data
ts_heatmap(working_hours_ts, title = "Mar 2006 - MAR 2023 Agg. Weekly Work Hours Index Indexed(2007=100)")
```

The dotted-red line is mean.  The black line is index value and a trend line in blue. The green periods are recessions. There is no doubt there an overall upward trend in the data and seasonality must be explored.

## Summary Stats Grouped Year - plot
```{r, echo = FALSE, warning= FALSE}
stats_year_base <- working_hours %>%
  #select(year, hours_worked_index) %>%
  group_by(year) %>%
  summarise(year, avg = mean(hours_worked_index), median = median(hours_worked_index),
            stand_dev = sd(hours_worked_index)  
            ) %>%
  ggplot(aes(x = reorder(year, avg), y = avg)) +
  geom_point() +
  geom_errorbar(aes(ymin = avg - stand_dev, ymax = avg + stand_dev)) +
  coord_flip() +
  labs(title = 'MAR 2006 - Mar2023: Annual Mean & Variance', subtitle = '', 
       y = "Index Value with Base Year 2007 = 100", x = '') +
  theme(axis.text.y=element_text(face="bold", color="black", size=10, angle=0),
      axis.ticks.y=element_blank(),
      axis.title = element_text(face = "bold", color="black", size=10),
      axis.text.x = element_text(face = "bold", color="black", size=10),
      panel.background =element_rect('White'),
      legend.position = "none")

stats_year_base

#interactive chart
ggplotly(stats_year_base)
```
This chart looks at the variance in index of hours worked by year from 2006-2023 and can shed some insight about variance of indexed values for working hours.

## Summary Stats Grouped Month - Plot
```{r, echo=FALSE, warning= FALSE}
stats_month_base <- working_hours %>%
  #select(year, month, hours_worked_index) %>%
  mutate(month_name = as.factor(month.abb[month])) %>%
  group_by(month_name) %>%
  summarize(month_name, avg = mean(hours_worked_index), median = median(hours_worked_index),
            stand_dev = sd(hours_worked_index)  
            ) %>%
  ggplot(aes(x = reorder(month_name, avg), y = avg)) +
  geom_point() +
  geom_errorbar(aes(ymin = avg - stand_dev, ymax = avg + stand_dev)) +
  coord_flip() +
  labs(title = 'MAR 2006 - Mar 2023 Variance by Month  Base 2007 = 100', subtitle = 'Min, Mean, Max', 
       y = "", x = '') +
  theme(axis.text.y=element_text(face="bold", color="black", size=10, angle=0),
      axis.ticks.y=element_blank(),
      axis.title = element_text(face = "bold", color="black", size=10),
      axis.text.x = element_text(face = "bold", color="black", size=10),
      panel.background =element_rect('White'),
      legend.position = "none")

stats_month_base

#interactive chart
ggplotly(stats_month_base)
```

Variance in index of hours worked by month from 2006-2023 provides insight about cycles in working hours.

## Boxplot by Month to Evaluate Seasonality
```{r, echo=FALSE, warning=FALSE}
# Boxplot for cycle associations by month
ts_plot_season <- function(x = x) {
season <- cycle(x)
season.factor <- factor(season)
ggplot() + 
  geom_boxplot(mapping = aes(x = season.factor,
                             y = x)) +
  labs(x = "Month", y =  "Index Hours Worked",
       title = "Seasonality/Cycles: Agg Weekly Hours Indexed(2007 = 100) reported monthly") +
  theme(axis.text.y=element_text(face="bold", color="black", size=10, angle=0),
      axis.ticks.y=element_blank(),
      axis.title = element_text(face = "bold", color="black", size=10),
      axis.text.x = element_text(face = "bold", color="black", size=10),
      panel.background =element_rect('White'),
      legend.position = "none")
}
raw_season <- ts_plot_season(working_hours_ts) +
  ggtitle("Raw Data Seasonality/Cycles by Month All Years, Base 2007 = 100")
raw_season  

# Interactive graph
ggplotly(raw_season)
```
This box plot is another method to look at potential seasonality by month from 2006-2023. The Q1 and Q4 are slightly higher than Q2 and Q3 as present in the box plot which is indicative of a cycle. First let's address the Trend and maybe the seasonality with taking the first difference. It is clearly evident that taking the first-difference of indexed hours worked is worth exploring.

## Add in First Difference
```{r}
# create First Difference of Hours Worked Index
working_hours_diff = diff(working_hours_ts)

## Comparison of First Difference vs. Raw Data
par(mfrow = c(2,1), mex = 0.6, cex = 0.8)
plot(working_hours_ts, main = 'Index of avg Hours Worked (Base = 2007 at 100) Red Line = Time-Series Mean', 
        xlab = 'Date', ylab = 'Index Value ',type = "l", col = 'blue')
    abline(h = mean(working_hours_ts), col = "red")

plot(working_hours_diff, main = 'First Difference of Working Hours', xlab = 'Date',
     ylab = 'First Difference Index Value')
     lines(working_hours_diff, col = 'blue')
     abline(h = mean(working_hours_diff), col = 'red')
```

We can see that using the first difference removes the trend with the COVID outlier remaining. Let's look at a histogram of raw data vs. first difference data. 

## Histogram data
```{r, echo = FALSE, warning=FALSE}
# Histogram - Basic 
hist_base <- gghistogram(working_hours_ts, fill = "blue", color = 'black', alpha = 0.50,
                    title ='Mar 2006 - MAR 2023', 
                    subtitle = 'Agg. Weekly Work Hours Index Indexed(2007=100)',
                    xlab = 'Index Value: Base (2007 = 100)', ylab = 'Frequency')  +
  geom_density(color = 'red' )

# Histogram - Basic for First Difference of Hours Worked Index
hist_diff <- gghistogram(working_hours_diff, fill = "blue", color = 'black', alpha = 0.50,
                    title ='First Difference: Mar 2006 - MAR 2023   n = 204', 
                    subtitle = 'Agg. Weekly Work Hours Index Indexed(2007=100)',
                    xlab = 'Index Value: Base (2007 = 100)', ylab = 'Frequency')  +
                    xlim(-5,5) +
  geom_density(color = 'red' )

# Combination of Histograms with Raw Data, First Difference & Second Difference
hist_combo <- ggarrange(hist_base, hist_diff, nrow = 2, label.y  = 0.3,
                        font.label = list(size = 8, color = "black", face = "bold", family = NULL))
plot(hist_combo)

# Interactive historgram raw data & first difference
subplot(ggplotly(hist_base), ggplotly(hist_diff))
```

Here we can see the distribution differences between the raw data and the first difference data. The first difference data has a more normal distribution indicating that the data is possibly stationary and that we can model on it using the regression assumption necessary to draw inferences. Let's look at boxplot once again and compare raw data vs. first difference of index of working hours.

## Boxplot of Raw vs. First Difference Data
```{r,echo=FALSE, warning=FALSE}
# First Difference of Hours Worked Index and Seasonality Check
first_diff_season <- ts_plot_season(working_hours_diff) +
  ggtitle("First Diffrence Data Seasonality/Cycles by Month All Years, Base 2007 = 100")
first_diff_season

# Combine Raw Data & First Difference
ggarrange(raw_season, first_diff_season, nrow =2)
```

The variance has decreased, let's look at seasonality.

## Scatter plot by Year to Evaluate Seasonality (Raw data vs. First Difference)
```{r, echo=FALSE}
## Seasonality check 
season_raw <- ggseasonplot(working_hours_ts) +
  ylab("Index Hours") +
  ggtitle("Raw:All Years Seasonal Plot") +
  theme_classic2()

# Interactive Chart
ggplotly(season_raw)

# First Difference of Hours Worked Index and Seasonality Check
season_first_diff <- ggseasonplot(working_hours_diff) +
  ylab("Index Hours") +
  ggtitle("First Difference: Seasonal Plot All Years") +
  theme_classic2()

# Interactive Chart
ggplotly(season_first_diff)

# Combined Plot of Raw vs. First Differenced Hours Worked Index
combo_diff_sec_diff_scatter <- ggarrange(season_raw, season_first_diff,
          nrow = 2, common.legend = TRUE, legend = 'right', label.x = '')
combo_diff_sec_diff_scatter

# Interactive Chart of Seasonality Raw Data & First Difference Hours Worked
subplot(ggplotly(season_raw), ggplotly(season_first_diff), nrows = 2, shareX = TRUE)
```
There are 17 periods for each month with April being lowest aggregated and indexed to 2007 with a value 99.9, and December was highest aggregated and indexed value of 102.9 hours against base 2007. Seasonality plot for all years and months demonstrates the Great Recession and Covid period as illuminated in purple line not like any other of the other lines plotting index of hours worked over all twelve months from 2006-2023.

## Decompose data to inspect trend, seasonal and random events
```{r, echo=FALSE}
decomp_work_hours_ts <- decompose(working_hours_ts, "additive")
plot(decomp_work_hours_ts)

# Interactive Charts
decomp_work_hours_ts <- ts_decompose(working_hours_ts, "additive", showline = TRUE)
decomp_work_hours_ts

# First Difference Hours Worked Index decomposition
decomp_work_hours_diff <- ts_decompose(working_hours_diff, "additive", showline = TRUE)
decomp_work_hours_diff
```

The width and height of seasonal cycles over time is predictable and trend is fairly linear with the first difference of hours worked, or seasonal variation is relatively constant over time. Thus, decomposition additively (Yt = Tt + St + Rt) seems appropriate. We'll check if differencing of seasonality required using nsdiffs() function.  

## Seasonal Differencing Check
```{r}
working_hours_diff %>% nsdiffs()
```

We see that seasonal differencing is not required for our time series, let's now check the correlograms.

## Raw & First Difference Plot the autocorrelation and partial autocorrelations
```{r, echo= FALSE}
# Correlogram of raw time series
acf_12_plot <- ggAcf(working_hours_ts, lag.max = 12,  
             main = "ACF Base Time Series")
pacf_12_plot <- ggPacf(working_hours_ts, lag.max = 12,
               main = "PACF Base Time Series")

acf_pacf_12_plot <- ggarrange(acf_12_plot, pacf_12_plot, nrow = 2) # lag = 12
acf_pacf_12_plot

# Correlogram of first difference index of hours worked
acf_12_diff <- ggAcf(working_hours_diff, lag.max = 12,  
             main = "First Difference ACF - Lag = 12")
pacf_12_diff <- ggPacf(working_hours_diff, lag.max = 12,
               main = "First Difference PACF - Lag = 12")

acf_pacf_12_diff <- ggarrange(acf_12_diff, pacf_12_diff, nrow = 2) # lag = 12
acf_pacf_12_diff

acf_pacf_combo <- ggarrange(acf_pacf_12_plot, acf_pacf_12_diff, nrow = 1, ncol = 2)
acf_pacf_combo

```

With ACF and PACF spikes at the second lag suggests that a combined ARMA model of order 2 may be appropriate to consider. The MA(2), AR(2) and ARMA(2,2) models are still intuitive models to further research for modeling as the PACF is alternating through lag periods. 

# Augmented Dickey-Fuller test on Differenced Data to Check for Stationarity.
```{r, echo=FALSE, warning=FALSE}
lag_order <- ndiffs(working_hours_ts, test = "adf")  # Using ADF test for lag order selection
lag_order
lag_order_check <- ndiffs(working_hours_diff, test = "adf")  # Using ADF test for lag order selection
lag_order_check
```
Taking the difference of working hours index values is sufficient for stationary time series.

```{r, echo=FALSE}
#DF test Urca library + adf.test
df_diff_data = ur.df(working_hours_diff, type = "none", selectlags = "AIC", lags =0)
summary(df_diff_data)
```

Dickey-Fuller suggests that we have stationary data now, as the p-value is below 0.01 and test statitic of -14.474 is less than critical value of -2.58 at 99 percent confidence interval, we can reject the null hypothesis that this data is not stationary.

## Phillips Perron Test
```{r, echo=FALSE}
pp.test(working_hours_ts)
pp.test(working_hours_diff)
```

Confirms data is stationary.

## KPSS Test
```{r, echo=FALSE}
kpss_base <- ur.kpss(working_hours_ts)
summary(kpss_base)

kpss_first_difference <- ur.kpss(working_hours_diff)
summary(kpss_first_difference)
```

The normal time series without differencing as a t-statistics of 3.2645, which is much higher than critical value at 10 pct significance-level.  When we difference working hours and complete KPSS, our t-statistic is .01174 and lower than critical value at 1 pct.  This confirms Dickey-Fuller that differencing hours worked makes the time series stationary.

# Model Fitting and Analysis (2,1,2)
```{r}
# Fit an ARMA model with order of 2 for both terms with the first difference.
model_ARMA212 = arima(working_hours_ts, order = c(2, 1, 2))
summary(model_ARMA212) # RMSE = 1.275151
coeftest(model_ARMA212)
autoplot(model_ARMA212)
BIC(model_ARMA212)

# Root test
if (all(abs(polyroot(c(1, -model_ARMA212$coef))) < 1)) {
  message("Model is invertible.")
} else {
  message("Model is not invertible.")
} 
```

```{r}
# R-Squared from Week 6-Chapter 8 practice problem set
n = length(working_hours_ts)
arma22_R2 = cor(fitted(model_ARMA212), working_hours_ts)^2  # 0.9618626
arma22_AR2 = 1 - (1-arma22_R2) * (n - 1) / (n - 4 - 1)
arma22_R2 # 0.9618898
arma22_AR2 # 0.9611276
```

```{r}
# Get the residuals from the ARIMA model
arma_residuals <- residuals(model_ARMA212)

y <- length(as.vector(working_hours_ts)) # length of working_hours_diff

# Calculate the total sum of squares (TSS)
mean_y <- mean(as.vector(working_hours_ts))
tss <- sum((as.vector(working_hours_ts) - mean_y)^2)

# Calculate the residual sum of squares (RSS)
rss <- sum(arma_residuals^2)

# Calculate the number of predictors or parameters in the model (p)
p <- length(model_ARMA212$coef)

# Calculate the number of observations (n)
n <- length(working_hours_ts)

# Calculate R-squared
rsquared <- 1 - (rss / tss)

# Calculate the adjusted R-squared
adj_rsquared <- 1 - ((1 - rsquared) * (n - 1) / (n - p - 1))

# Print the calculated R-squared and adjusted R-squared values
print(rsquared)

# adj_rsquared <- 1 - rsquared
# adj_rsquared
print(adj_rsquared)
```

```{r}
# Residuals check ACF/PACF
checkresiduals(model_ARMA212)

# Plot residuals in ACF/PACF
arma212_acf_residuals <- acf(model_ARMA212$residuals, main = "ACF Residuals")
arma212_pacf_residuals <- pacf(model_ARMA212$residuals, main = "PACF Residuals")

# combine ACF/PACF with residuals using qqnorm.
par(mfrow = c(3,1) , mex = 0.6, cex = 0.8, cex.main = .9)
plot(arma212_acf_residuals)
plot(arma212_pacf_residuals)
qqnorm(residuals(model_ARMA212), main = 'ARMA(2,1,2) Residuals')
qqline(model_ARMA212$residuals, col = 'red')
```

```{r}
# Q-Test
r_2_box_test <- Box.test(model_ARMA212$residuals, lag = 5, type = "Ljung")
r_2_box_test # X-squared = 0.22148, df = 5, p-value = 0.9989

QTest<-numeric(5)
for (i in 1:5){ 
  qt <- Box.test(model_ARMA212$residuals, lag=i, type="Ljung")
  QTest[i]=qt$statistic
} 

QTest 
plot(QTest, main = "ARMA(2,1,2) Q Test", xlab = "lag", ylab = "p-value")
abline(h = .05, col = "red", lty = 3)
```

```{r}
# Forecast 6 months
fcast_ARMA212 = forecast(model_ARMA212, h=6)
autoplot(fcast_ARMA212, include = 12, ylab = "Working hours - Base 2007 with 100") 
summary(fcast_ARMA212)

# Interactive Plot
fcast_ARMA212_plot <- plot_forecast(fcast_ARMA212, title = "ARMA(2,1,2) h =6", 
                                 Ytitle = "index-Base 2007 = 100", Xtitle="Date")
fcast_ARMA212_plot
```

So we have a reasonably good fit here with a ARMA(2,2) model the AIC is 689.72 which is relatively low, adjusted r-squared of 0.9611276, and phi parameters are both < 1, suggesting a good fit. As well RMSE is 1.2737 which suggests that this models predictions are roughly 1.27 units, or in our case hours, away from actual values. This is a good start.

The Ljung-Box statistic is used to see if all underlying population autocorrelations for the error may be zero. Our t-stat was 0.0015358 and p-value of 0.9968 given 5 lags, which is well above 0.05 -a significant threshold for non-zero autocorrelations that rejects null that residuals are independently distributed.

# AR(2)
```{r}
# Fit an AR model with order of 2 for both terms with the first difference.
model_AR210 = arima(working_hours_ts, order = c(2, 1, 0))
summary(model_AR210) # RMSE = 1.27648, MAE = 0.4587968, MPE = 0.08211823, MAPE = 0.4575043 
coeftest(model_AR210)
autoplot(model_AR210)
BIC(model_AR210)

# Root test
if (all(abs(polyroot(c(1, -model_AR210$coef))) < 1)) {
  message("Model is invertible.")
} else {
  message("Model is not invertible.")
}  #Not invertible
```

```{r}
# R-Squared from Week 6-Chapter 8 practice problem set
n = length(working_hours_ts)
ar2_R2 = cor(fitted(model_AR210), working_hours_ts)^2  # 0.9618626
ar2_AR2 = 1 - (1-ar2_R2) * (n - 1) / (n - 2 - 1)
ar2_R2
ar2_AR2
```

```{r}
# Get the residuals from the ARIMA model
ar_residuals <- residuals(model_AR210)

y <- length(as.vector(working_hours_ts))

# Calculate the total sum of squares (TSS)
mean_y <- mean(as.vector(working_hours_ts))
tss <- sum((as.vector(working_hours_ts) - mean_y)^2)

# Calculate the residual sum of squares (RSS)
rss <- sum(ar_residuals^2)

# Calculate the number of predictors or parameters in the model (p)
p <- length(model_AR210$coef)

# Calculate the number of observations (n)
n <- length(working_hours_ts)

# Calculate R-squared
rsquared <- 1 - (rss / tss)

# Calculate the adjusted R-squared
adj_rsquared <- 1 - ((1 - rsquared) * (n - 1) / (n - p - 1))

# Print the calculated R-squared and adjusted R-squared values
print(rsquared)
print(adj_rsquared)
```

```{r}
# Residuals check ACF/PACF
checkresiduals(model_AR210)

# Plot residuals in ACF/PACF
ar2_acf_residuals <- acf(model_AR210$residuals, main = "ACF Residuals")
ar2_pacf_residuals <- pacf(model_AR210$residuals, main = "PACF Residuals")

# combine ACF/PACF with residuals using qqnorm.
par(mfrow = c(3,1) , mex = 0.6, cex = 0.8, cex.main = .9)
plot(ar2_acf_residuals)
plot(ar2_pacf_residuals)
qqnorm(residuals(model_AR210), main = 'ARMA(2,1,0) Residuals')
qqline(model_AR210$residuals, col = 'red')
```

```{r}
# Q-Test
r_2_box_test <- Box.test(model_AR210$residuals, lag = 3, type = "Ljung")
r_2_box_test # X-squared = 0.24939, df = 3, p-value = 0.9692

QTest<-numeric(3)
for (i in 1:3){ 
  qt <- Box.test(model_AR210$residuals, lag=i, type="Ljung")
  QTest[i]=qt$statistic
} 

QTest 
plot(QTest, main = "AR2 Q Test", xlab = "lag", ylab = "p-value")
abline(h = .05, col = "red", lty = 3)
```

```{r}
# Forecast 6 months
fcast_AR21 = forecast(model_AR210, h=6)
autoplot(fcast_AR21, include = 12, ylab = "Working hours - Base 2007 with 100") 
summary(fcast_AR21)
fcast_AR21_plot <- plot_forecast(fcast_AR21, title = "ARMA(2,1,0) h =6", 
                                                                  Ytitle = "index-Base 2007 = 100", Xtitle="Date")
fcast_AR21_plot
```

The AIC is 685.56, both phi parameters are < 1, our adjusted r-squared is 0.9614188 and RMSE is 1.2769. Our Q-test using Ljung was 0.24938500 and p-value looked good at 0.9692 with three lags. The AIC was lower than ARMA 2,1,2 and adjusted r-squared was marginally better.  

# MA(2)
```{r}
# Fit an MA model with order of 2 for both terms with the first difference.
model_MA012 = arima(working_hours_ts, order = c(0, 1, 2))
summary(model_MA012) # RMSE = 1.275151
coeftest(model_MA012)
autoplot(model_MA012)
BIC(model_MA012)

# Root test
if (all(abs(polyroot(c(1, -model_MA012$coef))) < 1)) {
  message("Model is invertible.")
} else {
  message("Model is not invertible.")
}  #Not invertible

```

```{r}
# R-Squared from Week 6-Chapter 8 practice problem set
n = length(working_hours_ts)
ma2_R2 = cor(fitted(model_MA012), working_hours_ts)^2  # 0.9618626
ma2_AR2 = 1 - (1 - ma2_R2) * (n - 1) / (n - 2 - 1)
ma2_R2
ma2_AR2
```

```{r}
# Get the residuals from the ARIMA model
ma_residuals <- residuals(model_MA012)

y <- length(as.vector(working_hours_ts))

# Calculate the total sum of squares (TSS)
mean_y <- mean(as.vector(working_hours_ts))
tss <- sum((as.vector(working_hours_ts) - mean_y)^2)

# Calculate the residual sum of squares (RSS)
rss <- sum(ma_residuals^2)

# Calculate the number of predictors or parameters in the model (p)
p <- length(model_MA012$coef)

# Calculate the number of observations (n)
n <- length(working_hours_ts)

# Calculate R-squared
rsquared <- 1 - (rss / tss)

# Calculate the adjusted R-squared
adj_rsquared <- 1 - ((1 - rsquared) * (n - 1) / (n - p - 1))

# Print the calculated R-squared and adjusted R-squared values
print(rsquared)
print(adj_rsquared)
```

```{r}
# Residuals check ACF/PACF
checkresiduals(model_MA012)

# Plot residuals in ACF/PACF
MA012_acf_residuals <- acf(model_MA012$residuals, main = "ACF Residuals")
MA012_pacf_residuals <- pacf(model_MA012$residuals, main = "PACF Residuals")

# combine ACF/PACF with residuals using qqnorm.
par(mfrow = c(3,1) , mex = 0.6, cex = 0.8, cex.main = .9)
plot(MA012_acf_residuals)
plot(MA012_pacf_residuals)
qqnorm(residuals(model_MA012), main = 'ARMA(2,1,0) Residuals')
qqline(model_MA012$residuals, col = 'red')
```

```{r}
# Q-Test
r_2_box_test <- Box.test(model_MA012$residuals, lag = 3, type = "Ljung")
r_2_box_test # X-squared = 0.22148, df = 5, p-value = 0.9989 - No serial Correlations/residuals independently distributed

QTest<-numeric(3)
for (i in 1:3){ 
  qt <- Box.test(model_MA012$residuals, lag=i, type="Ljung")
  QTest[i]=qt$statistic
} 

QTest 
plot(QTest, main = "MA2 Q Test", xlab = "lag", ylab = "p-value")
abline(h = .05, col = "red", lty = 3)
```

```{r}
# Forecast 6 months
fcast_MA012 <- forecast(model_MA012, h=6)
autoplot(fcast_MA012, include = 12, ylab = "Working hours - Base 2007 with 100")
summary(fcast_MA012)

# Interactive Chart
fcast_MA012_plot <- plot_forecast(fcast_MA012, title = "ARMA(0,1,2) h =6", 
                                 Ytitle = "index-Base 2007 = 100", Xtitle="Date")
fcast_MA012_plot
```
The AIC is 685.25, much better than MA(1) and ARMA(2,2), but only marginally better than AR(2). The adjusted r-squared is 0.961485, just slighly lower than AR(2) and ARMA(2,2), and RMSE was 1.275489. The Ljung box test p-value looked good at 0.9886 at 3 lags.

Our preferred model is ________ because __________________________________.



# Step 2 DTC -- OUT OF SAMPLE --
# Forecasting Environment for Train/Test split: Estimation Sample and Prediciton Sample.
There are 204 observations and we'll be doing a 90% / 10% split, thus our estimation sample with have 184 observations and our prediction sample will have 21 observations. We'll be applying a fixed scheme that will produce only one estimate and does not allow for parameter updating.

# Data Split into Train & Test Samples
```{r}
# split of time-series base time-series
length(working_hours_ts)
train <- window(working_hours_ts,start=c(2006,3),end=c(2021,6)) # 184 observations
test <- window(working_hours_ts, start=c(2021,7),end=c(2023,3)) # 21 observations

# split of first difference time-series
length(working_hours_diff) # 204 observations in working_hours_diff time series
train_diff <- window(working_hours_diff, start=c(2006,4),end=c(2021,7)) # 184 observations for training
test_diff <- window(working_hours_diff, start=c(2021,8),end=c(2023,3)) # 20 observations for test
```

# ARMA(2,1,2) Using Base Time-Series
```{r, echo = FALSE}
arma212_train <- arima(train, order = c(2,1,2))
autoplot(arma212_train)
coeftest(arma212_train)
summary(arma212_train) # MSE = 1.77070394, RMSE = 1.330678, sigma^2 estimated as 1.78
# Coefficients:
#          ar1     ar2      ma1      ma2
#       0.1857  0.1082  -0.2218  -0.2726
# s.e.  0.4234  0.3667   0.4105   0.3649

arma212_forecast <- forecast(arma212_train, h = length(test))
accuracy(arma212_forecast)

# Error, Loss (Error^2), MSE and MPE test
error <- test - arma212_forecast$mean
loss <- error^2
mse_arma212 <- mean(error^2) # 27.10559
mpe_test <-lm(error~1) # 4.83, t = 11.11, p-value 5.25e-10
summary(mpe_test)
#IET <- lm(error~arma212_forecast) problems.  
#summary(IET)
checkresiduals(arma212_forecast)

# Train vs. Test Accuracy Metrics - Consolidated
errors_arma212 <- forecast::accuracy(arma212_forecast, test) %>%
  as.data.frame() 
errors_arma212
#                      ME     RMSE       MAE        MPE      MAPE      MASE         ACF1 Theil's U
# Training set 0.07429913 1.330678 0.4737119 0.06076164 0.4778019 0.1723317 -0.003449782        NA
# Test set     4.82960956 5.206303 4.8296096 4.26126071 4.2612607 1.7569646  0.834828738  10.37058

# Plots
auto_arma212_predicted_vs_actual <- autoplot(arma212_forecast) + autolayer(test)
auto_arma212_predicted_vs_actual

# Interactive Plots
arma212_interactive <- test_forecast(actual = working_hours_ts, forecast.obj = arma212_forecast, test = test)
arma212_interactive
```

## ARMA(2,1,2) Using First Difference Time-Series
```{r, echo=FALSE}
arma212_train_diff <- arima(train_diff, order = c(2,0,2))
autoplot(arma212_train_diff)
coeftest(arma212_train_diff)
summary(arma212_train_diff) # RMSE = 1.329969, sigma^2 estimated as 1.79

# Coefficients:
#          ar1     ar2      ma1      ma2  intercept
#       0.1989  0.1007  -0.2371  -0.2649     0.0560
# s.e.  0.4237  0.3657   0.4115   0.3651     0.0701

arma212_forecast_diff <- forecast(arma212_train_diff, h = length(test_diff))
arma212_forecast_diff

# Error, Loss, MSE and MPE test
error_diff <- test_diff - arma212_forecast_diff$mean
loss_diff <- error_diff^2
mse_arma212_diff <- mean(error_diff^2) # 0.2455598
mpe_test_diff <-lm(error_diff~1) # 0.268
summary(mpe_test_diff)
checkresiduals(arma212_forecast_diff)

# Train vs. Test Accuracy Metrics
errors_arma212_diff <- forecast::accuracy(arma212_forecast_diff, test_diff) %>%
  as.data.frame()
#                        ME      RMSE       MAE      MPE     MAPE      MASE          ACF1 Theil's U
# Training set 0.0008038631 1.3299691 0.4516580      NaN      Inf 0.6583489 -0.0006102248        NA
# Test set     0.2679991559 0.4955399 0.4066763 112.2334 112.2334 0.5927824 -0.1767881727 0.8677364

# # Residuals between model and Train Data
# T testing errors
errors_arma212_diff <- arma212_forecast_diff$residuals

# Plots
auto_arma212_diff_predicted_vs_actual <- autoplot(arma212_forecast_diff) + autolayer(test_diff)

# Interactive Plots
arma212_diff_interactive <- test_forecast(actual = working_hours_diff, 
                                          forecast.obj = arma212_forecast_diff,
                                          test = test_diff)
arma212_diff_interactive
```

## ARMA(2,1,0) Using Base Time-Series
```{r, echo=FALSE}
arma210_train <- arima(train, order = c(2,1,0)) 
autoplot(arma210_train)
coeftest(arma210_train)
summary(arma210_train) # RMSE = 1.334404, sigma^2 estimated as 1.79
# Coefficients:
#           ar1      ar2
#       -0.0262  -0.1600 *
# s.e.   0.0728   0.0726

# Forecast on test sample 
arma210_forecast <-forecast(arma210_train, h= length(test))
arma210_forecast

# Error, Loss, MSE and MPE test
error <- test-arma210_forecast$mean
loss <- error^2
mse_arma210 <- mean(error^2) # 24.57494
mpe_test <- lm(error~1) # 4.571
summary(mpe_test)
checkresiduals(arma210_forecast)

# Train vs. Test Accuracy Metrics
errors_arma210 <- forecast::accuracy(arma210_forecast, test) %>%
  as.data.frame()
#                      ME     RMSE       MAE        MPE      MAPE      MASE         ACF1 Theil's U
# Training set 0.06505855 1.334404 0.4638089 0.05273247 0.4675245 0.1687291 -0.007420601        NA
# Test set     4.57096340 4.957312 4.5709634 4.03185528 4.0318553 1.6628716  0.838859648   9.87256

# Stat test to Validate Results from Out of Sample Evaluation Model Accuracy
# T testing errors
errors_arma210 <- arma210_forecast$residuals

# Plots
auto_arma210_predicted_vs_actual <- autoplot(arma210_forecast) + autolayer(test)
auto_arma210_predicted_vs_actual

# Interactive Plots
arma210_interactive <- test_forecast(actual = working_hours_ts, 
                                     forecast.obj = arma210_forecast,
                                     test = test)
arma210_interactive
```

## ARMA (2,0,0) Using First Difference Time-Series
```{r, echo=FALSE}
arma200_train_diff <- arima(train_diff, order = c(2,0,0)) 
autoplot(arma200_train_diff)
coeftest(arma200_train_diff)
summary(arma200_train_diff)# RMSE = 1.333828 , sigma^2 estimated as 1.779
                                      # Coefficients:
                                      #           ar1      ar2  intercept
                                      #       -0.0278  -0.1611     0.0578
                                      # s.e.   0.0727   0.0724     0.0828        

# Forecast on test sample
arma200_forecast_diff <-forecast(arma200_train_diff, h= length(test_diff))
arma200_forecast_diff

# Error, Loss, MSE and MPE test
error <- test_diff-arma200_forecast_diff$mean
loss <- error^2
mse_arma200 <- mean(error^2) # 0.230621
mpe_test <- lm(error~1) # 0.2533
summary(mpe_test)
checkresiduals(arma200_forecast_diff)

# Train Vs. Test Accuracy Metrics
errors_arma200_diff <- forecast::accuracy(arma200_forecast_diff, test_diff) %>%
  as.data.frame()
#                        ME      RMSE       MAE      MPE     MAPE      MASE         ACF1 Theil's U
# Training set 0.0002714796 1.3338285 0.4432776      NaN      Inf 0.6461335 -0.005548084        NA
# Test set     0.2532795149 0.4802301 0.3934651 109.1354 109.1354 0.5735254 -0.220813887 0.8562286

# Stat test to Validate Results from Out of Sample Evaluation Model Accuracy
# T testing errors
errors_arma200_diff <- arma200_forecast_diff$residuals

# Plots
auto_arma200_diff_predicted_vs_actual <- autoplot(arma200_forecast_diff) +
  autolayer(test_diff)
auto_arma200_diff_predicted_vs_actual

# Interactive Plots
arma200_diff_interactive <- test_forecast(actual = working_hours_diff, 
                                          forecast.obj = arma200_forecast_diff,
                                          test = test_diff)
arma200_diff_interactive
```

## ARMA(2,0,0) Dynamic Library & Time Series
```{r, echo=FALSE}
# Fixed Scheme
fcast2<-numeric(21) #generate a vector of 21 
model<-dynlm(working_hours_ts ~ stats::lag(working_hours_ts,-1) + 
             stats::lag(working_hours_ts,-2), 
             start=c(2006,3), end=c(2021,6)) #fit AR(2), last 21 in t.s. stops

for (i in 1:21){ #start a for loop
  fcast2[i]<-coef(model)[1]+coef(model)[2]*working_hours_ts[183+i]+
             coef(model)[3]*working_hours_ts[182+i] # forecasted values each iteration
} 
  # Coefficients:
  #(Intercept)  stats::lag(working_hours_ts, -1)  stats::lag(working_hours_ts, -2)  
    #2.47647                           0.96502                           0.01104 

# how in the world are these coefficients of model so different from ARIMA(2,1,0)
# or ARIMA(2,0,0)

#f2 <- ts(fcast2, frequency = 12, start=c(2021,7)) # THIS MAYBE NOT NECESSARY!!!! ????


# create vectors to capture forecast error and loss for last 21 observations real vs forecast.
ferror2<-numeric(21) #generate a vector of 21 zeros
loss2<-numeric(21) #generate a vector of 21 zeros
for (i in 1:21){
  ferror2[i]<-working_hours_ts[184+i]- fcast2[i] #fill in forecasted values at the end of each iteration
  loss2[i] <-ferror2[i]^2
}

cbind(test,fcast2, ferror2, loss2)
MSE2 <- mean(loss2) #  0.4344058

mpetest <- lm(ferror2 ~ 1)
summary(mpetest)

IETest <- lm(ferror2 ~ fcast2)
summary(IETest)
checkresiduals(fcast2)
```

## ARMA(0,1,2) Using Base Time-Series
```{r, echo=FALSE}
arma012_train <- arima(train, order = c(0,1,2))
autoplot(arma012_train)
coeftest(arma012_train)
summary(arma012_train) # 1.332218, sigma^2 estimated as 1.784
# Coefficients:
#           ma1      ma2
#       -0.0411  -0.1765
# s.e.   0.0731   0.0745

arma012_forecast <- forecast(arma012_train, h = length(test)) # predict - n=21
arma012_forecast

# Error, Loss, MSE and MPE test
error <- test-arma012_forecast$mean
loss <- error^2
mse_arma012 <- mean(error^2) # 25.43779
mpe_test <- lm(error~1) # 0.2533
summary(mpe_test)
checkresiduals(arma012_forecast)

# Train vs. Test Accuracy Metrics
errors_arma012 <- accuracy(arma012_forecast, test) %>%
  as.data.frame()

# Basic Research for IET test - 
errors_arma012 <- arma012_forecast$residuals  # Residuals on testing fit - helpful for IET testing?
#IET_test <- lm(error ~ arma012_forecast)

# Plots
auto_arma012_train_predicted_vs_actual <- autoplot(arma012_forecast) +
  autolayer(test)
auto_arma012_train_predicted_vs_actual

arma012_interactive <- test_forecast(actual = working_hours_ts, 
                                 forecast.obj = arma012_forecast, test = test)
arma012_interactive
```

##  ARMA(0,1,2) Using First Difference
```{r}
arma002_train_diff <- arima(train_diff, order = c(0,0,2))
autoplot(arma002_train_diff)
coeftest(arma002_train_diff)
summary(arma002_train_diff) # 1.332218, sigma^2 estimated as 1.773
# Coefficients:
#           ma1      ma2  intercept
#       -0.0437  -0.1773     0.0572
# s.e.   0.0730   0.0741     0.0767

arma002_forecast_diff <- forecast(arma002_train_diff, h = length(test_diff)) # predict - n=21
arma002_forecast_diff

# Error, Loss, MSE and MPE test
error <- test_diff-arma002_forecast_diff$mean
loss <- error^2
mse_arma012 <- mean(error^2) # 0.230621
mpe_test <- lm(error~1) # 0.2533
summary(mpe_test)
checkresiduals(arma002_forecast_diff)

# Train vs. Test Accuracy Metrics
errors_arma002_diff <- accuracy(arma002_forecast_diff, test_diff) %>%
  as.data.frame()

# Stat test to Validate Results from Out of Sample Evaluation Model Accuracy
# T testing errors
errors_arma002 <- arma002_forecast_diff$residuals  # Residuals on testing fit

# Plots
auto_arma002_train_diff_predicted_vs_actual <- autoplot(arma002_forecast_diff) +
  autolayer(test_diff)
auto_arma002_train_diff_predicted_vs_actual

arma002_interactive <- test_forecast(actual = working_hours_diff, 
                                 forecast.obj = arma002_forecast_diff, 
                                 test = test_diff)
arma002_interactive

```

# Simple Average 4 Naive Forecast
```{r}
#Model III (Average-4)
fcast_MA4 <-numeric(21) # estimation sample = 20

for (i in 1:21){ 
  fcast_MA4[i]<-(working_hours_ts[181+i]+working_hours_ts[182+i]+
              working_hours_ts[183+i]+working_hours_ts[184+i])/4 #forecast is the average of the last 4 observations
}

error <- test-fcast_MA4
loss <- error^2
mse_MA4 <- mean(error^2) # 0.3365476
mpe_test_MA4 <- lm(error~1) # 0.5024 
summary(mpe_test_MA4) 
checkresiduals(fcast_MA4)
IET_test <- lm(error ~ fcast_MA4)
summary(IET_test)
errors_MA4 <- accuracy(fcast_MA4, test) %>%
  as.data.frame()
#                ME      RMSE       MAE       MPE      MAPE      ACF1 Theil's U
# Test set 0.502381 0.5801272 0.5095238 0.4487045 0.4549592 0.2833054  1.134857

# Plots

```


###### PROFESSOR/SURPLUS


```{r}

comb<-lm(g0~(fcast1)+(fcast2)+(fcast3)) 
summary(comb)

fcast4<-numeric(21) #generate a vector of 20 zeros
ferror4<-numeric(21) #generate a vector of 20 zeros
loss4<-numeric(21) #generate a vector of 20 zeros

fcast4 <- comb$fitted.values
ferror4 <- g0-fcast4
loss4 <-ferror4^2

MSE4 <- mean(loss4)

```